The Hydrogen Epoch of Reionization Array Dish I: Beam Pattern Measurements and Science Implications

### 2015-11-06 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
remove aarons big file, and minor beam paper updates

This is the XXth in a series of four papers detailing the HERA element. We focus on the 
angular response of the dish and its implications for power spectrum measurements, 
following reflectometry measurements of the dish frequency response by Patra et al. 
(submitted), and simulations by Ewall-Wice et al. (submitted), as well as detailed 
foreground simulations for HERA by Thyagarajan et al. (submitted). A general description to the design of the 
HERA experiment from an engineering point of view is given by DeBoer et al. (submitted). In essence, we 
require a large collecting area for
 sensitivity and minimal sidelobes and horizon response without incurring the large cost per collecting 
area of very large dishes. A dish is preferred to a large phased array as it has fewer degrees 
of freedom and reduced potential of antenna-to-antenna variation (Neben et al 2015b, 
submitted). These factors naturally lead to a 14\,m diameter parabolic dish with a dipole 
feed suspended at prime focus. The 352 dishes are positioned in a compact, hexagonal 
array permitting redundant baseline calibration and coherent integration in $
\vec{k}$ space \citep{omniscope,ali2015}. 
%The smaller field of view of the HERA dish relative to that of the PAPER dipole or the MWA tile does not limit sensitivity in Fourier space as most leverage on high $k$ modes is from line of sight modes anyway \citep{PoberNextGen}.

>>>>

This is the first paper in a series of four papers detailing the HERA element. We focus on the 
angular response of the dish and its implications for power spectrum measurements. The three companion 
papers present reflectometry measurements (Patra et al., submitted) and simulations (Ewall-Wice et al., 
submitted) of the dish frequency response, as well as detailed 
foreground simulations for HERA (Thyagarajan et al., submitted). A general description to the design of the 
HERA experiment from an engineering point of view is given by DeBoer et al. (submitted). In essence, we 
require a large collecting area for
 sensitivity and minimal sidelobes and horizon response without incurring the large cost per collecting 
area of very large dishes. A dish is preferred to a large phased array as it has fewer degrees 
of freedom and reduced potential of antenna-to-antenna variation (Neben et al 2015b, 
submitted). These factors naturally lead to a 14\,m diameter parabolic dish with a dipole 
feed suspended at prime focus. The 352 dishes are positioned in a compact, hexagonal 
array permitting redundant baseline calibration and coherent integration in $
\vec{k}$ space \citep{omniscope,ali2015}. 
%The smaller field of view of the HERA dish relative to that of the PAPER dipole or the MWA tile does not limit sensitivity in Fourier space as most leverage on high $k$ modes is from line of sight modes anyway \citep{PoberNextGen}.
